Multi-Resolution Neural Field Estimation

### 2011-03-12 Multiresolution_framework/ltx/manuscript.tex

The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a). No assumptions where made about the shape of the kernel. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The large standard deviation is due to the high number of parameters need to be estimated. The small error in the estimate is attributed to the MRA of the system used to form the estimator. \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/fig1.pdf}
		\caption{Actual (gray) and estimated (black) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, $RMSE = 1.93$. (b) $j=1$, $n_x=33$, $RMSE = 1.39$. (c) $j=2$, $n_x=65$, $RMSE = 0.90$. (d) $j=3$, $n_x=131$, $RMSE = 0.78$. (e) $j=4$, $n_x=263$, $RMSE=0.78$.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/fig2.pdf}
		\caption{Connectivity kernel estimate. (a) The actual kernel is shown with the black solid line. The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.). (b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$.}
	\label{fig:KernelEstimate}
\end{figure}
% \caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape. This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy. Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling. It is thought that the dynamics and connectivity structure differs at different spatial scales~\cite{Qubbaj2009,Breakspear2005}. %\dean{This is a test to see if we can fit something about Breaky's paper in here. It would be nice to slot something in here because he used wavelets.}

>>>>

The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}(a). No assumptions where made about the shape of the kernel. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The large standard deviation is due to the high number of parameters need to be estimated. The small error in the estimate is attributed to the MRA of the system used to form the estimator. \figurename{\ref{fig:KernelEstimate}}(b) and (c) shows the kernel scaling and wavelet functions, respectively.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/fig1.pdf}
		\caption{Actual (gray) and estimated (black) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, $RMSE = 1.93$. (b) $j=1$, $n_x=33$, $RMSE = 1.39$. (c) $j=2$, $n_x=65$, $RMSE = 0.90$. (d) $j=3$, $n_x=131$, $RMSE = 0.78$. (e) $j=4$, $n_x=263$, $RMSE=0.78$.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/fig2.pdf}
		\caption{\parham{Connectivity kernel estimate. (a) The actual kernel and its components are shown by solid and dashed black lines respectively. The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.). (b)-(c) Kernel scaling and wavelets functions, respectively, at $j=1$ used in estimation algorithm.}}
	\label{fig:KernelEstimate}
\end{figure}
% \caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel and key developments of the paper include the multi-resolution FEM representation of the neural field, and the estimator for an intracortical connectivity kernel with an arbitrary shape. This work is significant, as the ability to create patient specific neural field models has the potential to contribute to our understanding and improve treatment of diseases resulting from abnormal neurodynamics, such as epilepsy. Other groups have previously highlighted the importance of a multi-resolution approach in neural field modeling. It is thought that the dynamics and connectivity structure differs at different spatial scales~\cite{Qubbaj2009,Breakspear2005}. %\dean{This is a test to see if we can fit something about Breaky's paper in here. It would be nice to slot something in here because he used wavelets.}
